\begin{center}
\begin{longtable}[c]{|p{3cm}|p{7.5cm}|p{7.5cm}|p{7.5cm}|}

\caption{Past incidents that involved the largest hazard and operation in Solvay plants}
\hline
\rowcolor[HTML]{CBCEFB} 
\textbf{Incident} & \textbf{Description} & \textbf{Consequences} & \textbf{Lessons   Learnt}   \hline

\hline
The Toxic White Beaches of Rosignano \citep{whitebeaches}&
  
The Solvay chemical plant in Rosignano   had been disposing their by-products     (mixture of calcium chloride   and limestone) in the sea.Many toxic   chemicals are mixed in with   the CaCl$_2$ e.g. mercury, arsenic,   cadmium, chromium, lead and ammonia,   which are harmful to humans and   animals. This is because limestone (main  feed in the Solvay process) has impurities  consisting of heavy metals. &
  
Due to the disposal of toxic   chemicals in the beach, the   Spiagge Bianche is among   the 15 most polluted coastal   sites in the Mediterranean Sea.   Between 2008 and 2010,   the town recorded a mortality   rate higher than the regional   average for the same period,   increasing by 2.2 \% for men   and 8.3 \% for women.   The frequency of tumours   and premature mortality (under   age 65) are both above the   regional average by several   percentage points. &
  
The purer the limestone   used in the Solvay  process,   the more suitable the limestone   is for lessening the impact from    the production of soda ash on   the environment. It is also   necessary to make sure that if   by-products are disposed in   the sea, they must  be purified from   toxic chemicals to not contaminate   the waterway.  \hline
TATA Chemicals Incidents \citep{TATA1}, \citep{TATA2} &
Operation of the   plant by   means of unsafe work methods.   Another incident happened on   March 12, 2021, when a large fire     was ignited in the TATA Chemicals   plant which was caused by   malfunctioning of electrical equipment   within an industrial building. A contractor   employee suffered chemical burns when   he was engulfed in hot caustic lime dust.   In addition, a worker fell from a walkway   8 feet high and became trapped to his waist. &
Workers from the TATA   Chemicals factory got   injured due to the lack   of safety measures in   the plant. TATA Chemicals   was fined with   almost \pounds 350,000.&
Both incidents could have   been avoided with regular   assessment of risks and   inspection of work equipment .  
\hline
\hline

Imperial Sugar Company   Dust Explosion and Fire  &
The explosion was fueled   by massive accumulations   of combustible sugar dust   throughout the packaging building. On   February 7, 2008, a huge explosion   and fire occurred at the Imperial Sugar   refinery northwest of Savannah, Georgia. &
This explosion caused 14   deaths and injuring 38 others,   including 14 with serious and   life-threatening burns.&
Combustible dust hazard   awareness should be incorporated   into employee and member   companies’ training programs.   Combustible dust characteristics,   especially ignition energy and   minimum explosible concentration   should also be studied.  In addition,   best practices for minimising   dust accumulation should be   incorporated as well as safe   housekeeping practices.   Finally, specific combustible   dust inspection requirements   should be implemented.  \hline

\end{longtable}
\end{center}